\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-23 ACC16.2.tex
working on simulation section

\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
	J = \begin{bmatrix}
	\num{5.571e-3} & \num{6.177e-5} & \num{-2.503e-5} \\
	\num{6.177e-5} & \num{5.571e-3} & \num{1.001e-5} \\
	\num{-2.503e-5} & \num{1.007e-5} & \num{1.051e-2}
	\end{bmatrix} \, .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 10 \, .
\end{gather*}
A body fixed sensor is defined as
\begin{gather*}
	r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix} \, ,
\end{gather*}
while multiple inequality constraints are defined in~\cref{tab:constraints}.

The initial and desired states are defined using Euler angles as~\cite{shuster1993},
\begin{gather*}
	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
	R_d = ROT3(\ang{90}) \, , \quad \Omega_d = 0 \, .
\end{gather*}

Present three cases

>>>>

\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
	J = \begin{bmatrix}
	\num{5.571e-3} & \num{6.177e-5} & \num{-2.503e-5} \\
	\num{6.177e-5} & \num{5.571e-3} & \num{1.001e-5} \\
	\num{-2.503e-5} & \num{1.007e-5} & \num{1.051e-2}
	\end{bmatrix} \, .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} \parenth{0.9,1.1,1.0}\, , \quad k_R = 0.4 \, , \quad	k_\Omega = 0.296 \, ,\\
	c = 1.0 \, , \quad k_\Delta = 0.5 \, , \quad \alpha = 15 \, .
\end{gather*}
A body fixed sensor is defined as
\begin{gather*}
	r = \begin{bmatrix} 1 & 0 & 0 \end{bmatrix} \, ,
\end{gather*}
while multiple inequality constraints are defined in~\cref{tab:constraints}.
The simulation parameters are chosen to emulate those found in~\cite{lee2011b}.
\begin{table}[htbp]
\begin{center}\begin{tabular}{lc}
Constraint Vector & Angle \\ \hline \hline 
\(\begin{bmatrix} 0.174 &-0.934 & -0.034 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} 0 & 0.7071 & 0.7071 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} -0.853 & 0.436 & -0.286 \end{bmatrix}\) & \ang{40} \\ \hline 
\(\begin{bmatrix} -0.122 -0.140 -0.983 \end{bmatrix}\) & \ang{20}\end{tabular} 
\caption{Simulation Parameters}
\end{center}
\label{tab:constraints}
\end{table}
The initial and desired states are defined using Euler angles as~\cite{shuster1993},
\begin{gather*}
	R(0) = I \, , \quad \Omega(0) = 0 \, ,\\
	R_d = ROT3(\ang{225}) \, , \quad \Omega_d = 0 \, .
\end{gather*}

We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}
We assume a fixed disturbance of 
\begin{gather*}
	\Delta = \begin{bmatrix} 0.06 & 0.06 & 0.09 \end{bmatrix}^T \, ,
\end{gather*}
with the function \( W(R,\Omega) = I \).
This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
Present three cases
